---
title: "The Black Road RPG v1.39b7 --- Changelog"
author: "Unholy0ne and Alteisen (Av3n)"
format: html
toc: true
toc-depth: 2
toc-location: left
fontsize: "18px"
page-layout: full
embed-resources: true
css: "TBR.css"
editor: 
  markdown: 
    wrap: 72
---

# General

-   Effects that increase **Spell Power** with a multiplier now stack
    multiplicatively (previously they stacked additively)
-   Upon purchasing **Vigorous** <small>(Familiar Skill)</small>, your
    current % health is set to the % health you had prior to purchasing
    it
-   Updated the code that handles the item restrictions
-   Triggered error messages no longer uses Wc3's on-screen text frame
-   Updated **Saving and Loading** <small>(F9)</small> entry to better
    describe where Wc3's places save/load codes on macOS
-   If multiple items grant a healing effect on auto-attacks, TBR now
    only prints a single floating text element that displays the total
    amount of healing. <small>(Previously TBR would print multiple
    floating text elements)</small>

## Armor and Resist

*Resist* is a new visible stat that functions like *Armor*, except for
magical damage! This change provides a straightforward framework for
magical damage resistance stacking. The formula for magical damage
reduction (%) granted by *Resist* is

$$
\text{Magical D.R.} ~ (\%) =  \frac{0.005 \times \text{Resist}}{1 + 0.005 \times \text{Resist}}.
$$You can view the magical damage reduction (%) by hovering over the
*Resist* stat in the game UI (underneath the *Armor* stat).

Consequently, the constant for physical damage reduction (%) granted by
*Armo*r was reduced to 0.5% (previously 2%). This changes the formula
to:

$$
\text{Physical D.R.} ~ (\%) =  \frac{0.005 \times \text{Armor}}{1 + 0.005 \times \text{Armor}}.
$$

Furthermore, this means that **all** physical damage from any source
will now be reduced by the physical damage reduction (%) granted by
*Armor* (in addition to armor type).

## Auto-attack types

Auto-attacks are now classified as physical damage or magical damage
with the introduction of *Resist*. We will continue using two icons for
physical auto-attacks, but only a single icon is used for magical
auto-attacks. Lastly, the following <u>notable</u> changes have been
made to the auto-attack types of playable characters. Please see the
[Forces of Hell] section for auto-attack type changes to non-player
characters.

::: columns
::: column
**Classes with *physical* auto-attacks**

-   Warlord
-   Temple Guardian
-   Spartan Warrior
-   Assassin
-   Barbarian
-   Ranger
:::

::: column
**Classes with *magical* auto-attacks**

-   Cleric
-   Khaos Champion
-   Druid
-   Magician
-   Guardian of Nature
-   Warlock
:::
:::

## Armor types

The non-exclusive armor types for non-player characters have been
applied to playable characters with the introduction of *Resist*. This
change includes revising the original three armor types and introducing
an additional armor type for a total of four armor types for playable
characters and NPCs.

-   Heavy Armor: 20% additional physical damage reduction
-   Medium Armor: 10% additional physical *and* magical damage reduction
-   Warded Armor: 20% additional magical damage reduction
-   Light Armor: No additional physical damage reduction

Lastly, the following <u>notable</u> changes have been made to the armor
types of playable characters. Please see the [Forces of Hell] section
for armor type changes to non-player characters.

::: columns
::: column
**Classes with *heavy* armor**

-   Barbarian
-   Spartan Warrior
-   Khaos Champion
:::

::: column
**Classes with medium armor**

-   Guardian of Nature
-   Temple Guardian
-   Druid
:::

::: column
**Classes with *warded* armor**

-   Cleric
-   Warlock
-   Magician
:::

::: column
**Classes with *light* armor**

-   Ranger
-   Assassin
-   Warlord
:::
:::

## Essence

Introduced a new resource, **Essence**, that will be used as a resource
to progress your regalia. Loading in a [pre-1.39b7]{.underline}
character will grant the following:

-   Class regalia component: 5 Essence
-   Class regalia: 25 Essence *and* your character's base regalia item
-   Olympian regalia component: 250 Essence
-   Olympian regalia: 1000 Essence *and* a Gemstone of the Olympians

Killing the following notable enemies grants **Essence** to player
characters if their level is greater than or equal to the enemies'
level:

::: columns
::: column
-   Themis: 5 Essence
-   Hallowed One: 5 Essence
-   Cronus: 10 Essence
-   Medusa: 16 Essence
-   Shadowslayer: 19 Essence
-   Uranus: 19 Essence
-   Rhea: 32 Essence
-   Persephone: 44 Essence
:::

::: column
-   Hydra: 44 Essence
-   Oceanus: 50 Essence
-   Gaea: 75 Essence
-   Ladon: 84 Essence
-   Midas: 106 Essence
-   Sphinx: 106 Essence
-   Hades: 145 Essence
-   Hyperion: 205 Essence
:::
:::

## Quests

-   Increased the width of the <u>Quest Board</u> to no longer truncate
    quests that tracks a non-count objective
-   **Quest Helper** now always pings the location of the **Strange
    Note** <small>(Serius)</small> once it is discovered
-   Once **Captain Sepheus** <small>(Calliope)</small> is discovered,
    the chance to drop **Tattered Patch of Cloth** has been increased to
    26% (from 10%)
-   **History's Teachings** <small>(Dolios)</small> now presents two
    count objectives on the <u>Quest Board</u> to differentiate between
    the artifacts and the **Pactolus' Essence** objectives (previously
    one count objective)
-   Updated the quest levels of the following quests:

::: {.columns style="margin-left: 2.5%;"}
::: {.column width="48.75%"}
-   Lord of Nature <small>(Serius)</small>: 15 → 25
-   Lord of Justice <small>(Serius)</small>: 30 → 40
-   Lord of Death <small>(Serius)</small>: 40 → 55
-   Lord of the Sky <small>(Serius)</small>: 45 → 70
-   Queen of Sacrifice <small>(Serius)</small>: 55 → 85
-   Lord of the Sea <small>(Serius)</small>: 70 → 100
:::

::: {.column width="48.75%"}
-   Mother of the Sea <small>(Serius)</small>: 85 → 115
-   Lord of the Isles <small>(Gorgias)</small>: 60 → 70
-   A Rare Specimen <small>(Damien)</small>: 85 → 120
-   Speak with Heletes <small>(Heletes)</small>: 70 → 165
-   Restoring the Key <small>(Heletes)</small>: 85 → 165
:::
:::

## Personal Quests

Personal quests appear once per character until completed and are
automatically discovered once certain conditions are met. Information
about the quest is presented next to the Idle Familiar icon. Mousing
over the icon displays a tooltip with the current objective of the
quest, and clicking the icon pings the location of the current
objective.

+---------------------------------------------------------------+
| **Heletes' Boon\                                              |
| **This personal quest directs you on how to craft your        |
| regalia once you hit Lvl 30 *or* if you loaded a 1.39b6       |
| player character with regalia equipped.                       |
+---------------------------------------------------------------+
| **Heletes' Ingenuity\                                         |
| **This personal quest directs you on how to enhance your      |
| regalia for the first time once you hit Lvl 45 or higher with |
| *at least* one Essence.                                       |
+---------------------------------------------------------------+

This particular style of questing is an experimental addition to the
map. If the reception is positive, this may give us an idea of how to
push questing in TBR in the *very* distant future.

## Game Messages, Typos, & Typesetting

-   **Rejuvenation** <small>(Druid)</small>: Addressed the grammar issue
    with the ability tooltip
-   **Cataclysm** <small>(Guardian of Nature)</small>: Typesetting in
    spell level increase UI
-   **Walk in the Shadows** <small>(Assassin)</small>: Improved the
    description of mana regeneration mechanic.
-   **Pray** <small>(Temple Guardian)</small>: Tweaked the description
    of the ability tooltip.
-   **Tome of Stat Increase +X** <small>(Books & Forces of
    Hell)</small>: Improved the description of mechanic
-   Updated the game message that prints when the **Gates of Hell**
    become vulnerable
-   **Gaea's** form change mechanic prints game messages that are now
    timed for 5 seconds
-   **Cerberus'** pull mechanic prints game messages that are now timed
    for 5 seconds
-   Updated the colour code for class items to use a *slightly*
    different purple

# Bug Fixes

-   If **Atlas** is reset during the *Berserk* phase, it no longer
    permanently removes his ability to enter the *Berserk* phase in
    subsequent retries
-   **Cronus'** reset now works as intended
-   **Rhea's** reset now works as intended
-   Defeating **Gaea** now checks whether the defeated form is in the
    arena. If the defeated form is not in the arena, items instead spawn
    in the centre of **Gaea's** arena rather than in the "storage" zone
-   **Sphinx** can no longer target heroes under an *Auto-Life* effect
    with her *Entomb* mechanic
-   If **Sphinx** is reset during the *Vengeful Gaze* phase, it no
    longer permanently removes her ability to auto-attack in subsequent
    retries
-   The triggered component of **Aeacus'** *Life Drain* was recoded to
    mitigate the chances of a crash because of enhanced auto-attacks
-   `-save`/`-s` without a filename now uses the player character's
    exact class name *in English*
-   Addressed a regression in the previous `-roll`/`-r` functionality.
    You can now initiate a `-roll`/`-r` without requiring a string and
    `-roll`/`-r` to add to the leaderboard without requiring trailing
    characters, e.g. trailing whitespace
-   **Frost Fire Orb** <small>(Magician)</small> trail component now
    deals damage over time as intended
-   The tooltip for **Sadism** <small>(Warlock)</small> while it is on
    cooldown now matches the tooltip while it is *not* on cooldown

# Heroes

## Assassin

*Assassinate*, *Dancing Dagger*, *Eviscerate* and *Walk in the Shadows*
have received updated FX

## Spartan Warrior

*Phalanx*

> -   Rewrote the description to state how much mana is drained per
>     second and to make it clear that it only affect other players'
>     heroes
> -   *AoE* nerfed to 450. <small>(Previously 500)</small>
> -   *Movement speed reduction* nerfed to 50% / 35%. <small>(Previously
>     20% / 20%)</small>
> -   *Evasion* bonus nerfed to 25% / 30%. <small>(Previously 35% /
>     40%)</small>
> -   The M*agic Resistance* bonus of 35% / 40% is converted to a
>     *Resist* bonus of 65 / 85

## Temple Guardian

*Gift of Zeus*

> -   *Armor* bonus nerfed to 10 / 15 / 20 / 30 / 40 / 50 / 65 / 80.
>     <small>(Previously 20 / 30 / 40 / 50 / 60 / 70 / 85 / 100)</small>
> -   *Magic Resistance* bonus of 33% is converted to a *Resist* bonus
>     of 10 / 15 / 20 / 30 / 40 / 50 / 65 / 80

# Items

*Item Abilities*

> -   Evasion---Gain 5 / 10 / 15 / 20 / 25 % Evasion.
> -   Mana Regeneration---­Gain 10 / 20 / 30 / 40 / 50 % increased Mana
>     Regeneration.
> -   Bloodthirsty---Dealing fatal damage to an enemy increases
>     auto-attack damage by 10% for the next 8 seconds

*Ankh of Reincarnation* <small>(Alchemy)</small>, *Draught of the
Phoenix* <small>(Alchemy)</small>, *Immortal Armor of Hephaestus*
<small>(Master Metalsmith Heletes)</small>, *Chestguard of Aphrodite's
Champion* <small>(Armorsmith)</small>, and *Plates of the Ancient*s
<small>(Champion's Armory)</small>

> These items now have their "Ankh of Reincarnation" effect reclassified
> as the *Auto-Life* item ability

*Ares' Bloodthristy Spear* <small>(Master Metalsmith Heletes)</small>

> Eternal Hunger's maximum health degeneration nerfed to 1% (from
> 0.75%), and its current health threshold buffed to 5% (from 1%)

*Sword of the Olympians* <small>(Master Metalsmith Heletes)</small>

-   Item has been redesigned now that it is no longer part of the
    **Regalia Progression System**

> Increases Attack Damage by 100 and Attack Speed by 150%. Grants
> Versatile and Olympian.
>
> Versatile---Increases the hero's primary attribute by 75.
>
> Olympian---Your auto-attacks now deal 50% physical and 50% magical
> damage instead.
>
> Requires Level 165

*Ring of Regret* <small>(Midas)</small> and *Midas' Band of Vigor*
<small>(Metalsmith Galen)</small>

> *Magic Protection* item ability nerfed to:
>
> -   ≤ 24999: Reduces magical damage by 400. <small>(Previously
>     4000)</small>
>
> -   ≤ 49999: Reduces magical damage by 200. <small>(Previously
>     2000)</small>
>
> -   ≥ 50000: Reduces magical damage by 100. <small>(Previously
>     1000)</small>

*Amulet of Protection* <small>(Artifacts)</small>

> Evasion bonus nerfed to 10%. <small>(Previously 20%)</small>

*Silenus' Talisma*n <small>(Midas)</small> and *Midas' Pendant of
Wisdom* <small>(Metalsmith Galen)</small>

<!--# The Enfeeble proc was not entirely correct (stochastically) at being truly 10%, especially for a DoT type spell. To ratify this, Lower Resist has been updated to the following:<br> -->

<!--# <blockquote>Lower Resist—Spells have a 8% chance to Enfeeble I their target(s) for 8 seconds, reducing its Magic Resistance by 5%. If Lower Resist was applied by a spell-enhanced auto-attack or damage over time effect, it cannot be applied by either spell type for the next 12 seconds.</blockquote> -->

<!--# This is a functional change. What this means is that each tick of a DoT spell and any two-part spell now has a 10% chance to proc Lower Resist. The lock-out only applies if to spells which can proc Lower Resist via an auto-attack enhancing spell or DoT. However, the lock-out does not prevent one-off, two-part etc. spells from applying the Lower Resist proc -->

## Resist Related Changes

*Lesser Ether Dust, Ether Dust, Greater Ether Dust,* and *Superior Ether
Dust* <small>(Goldsmith)</small>

> The Ether Dust line of consumables now grant 10 / 20 / 35 / 50 Resist
> for 10 minutes. <small>(Previously a 1000 / 3000 / 8000 / 20000 magic
> damage shield for 10 minutes)</small>

*White Dragonscale Ring*, *Green Dragonscale Ring*, and *Red Dragonscale
Ring* <small>(Ladon)</small>

> The *Magic Resistance* bonus of 15% is converted to a *Resist* bonus
> of 35

*White Dragonscale Ring of Addiction*, *Green Dragonscale Ring of
Addiction*, and *Red Dragonscale Ring of Addiction* <small>(Metalsmith
Zoticus)</small>

> The *Magic Resistance* bonus of 20% is converted to a *Resist* bonus
> of 50

*Talisman of Serious Addiction* and *Warrior's Talisman of Serious
Addiction* <small>(Champion's Armory)</small>

> The *Magic Resistance* bonus of 25% is converted to a *Resist* bonus
> of 65

*Bright Silver Shinguards* and *Bright Silver Bracers*
<small>(Rare)</small>

> The *Magic Resistance* bonus of 20% is converted to a *Resis*t bonus
> of 50

*Bright Silver Plates* <small>(Metalsmith Galen)</small>

> The *Magic Resistance* bonus of 30% is converted to a *Resist* bonus
> of 85

*Adamantium Helm* <small>(Armorsmith)</small>

> The *Magic Resistance* bonus of 35% is converted to a *Resist* bonus
> of 100

I*ron Will of Hephaestus* <small>(Goldsmith)</small>

> -   *Health* bonus buffed to 1000. <small>(Previously 900)</small>
> -   Health Regeneration nerfed to 10. <small>(Previously 25)</small>
> -   Now grants a *Resist* bonus of 25. <small>(Previously an active
>     that grants a 10000 magic damage shield)</small>

*Shield of Zeus* <small>(Goldsmith)</small>

> -   No longer grants a *Health* bonus of 900
> -   Now grants a *Resist* bonus of 25. <small>(Previously an active
>     that grants a magic immunity shield).</small>

*Towering Shield of Athena* <small>(Master Metalsmith Heletes)</small>

> -   Updated the typesetting of the tooltip and assigned item ability
>     names for each non-standard bonus
> -   The *Magic Resistance* bonus of 50% is converted to a *Resist*
>     bonus of 175
> -   *Towering Defense*, the auto-attack damage block, is nerfed to
>     50000 damage. <small>(Previously 200000)</small>
> -   The *AoE* of *Protection Aura's* is nerfed to 450.
>     <small>(Previously 900)</small>
> -   The *AoE* of *Turn the Tide*, the full health and mana restore
>     active, is nerfed to 450. <small>(Previously 900)</small>

## Regalia Progression System Update

Set items for each class and the Olympian regalia items, except for the
*Sword of the Olympians*, have been removed. Instead, the regalia can be
crafted from Lvl 30 onwards and enhanced from Lvl 45 onwards. The
progression requirements for each tier regalia are:

+--------------------------------+---------------------------------+
| **Tier I** <small>Lvl          | **Tier II** <small>Lvl          |
| 30</small>                     | 45</small>                      |
|                                |                                 |
| Requires                       | Requires                        |
|                                |                                 |
| -   Titan Fibre                | -   Tier I                      |
| -   Titan Ore                  | -   5 Essence                   |
+--------------------------------+---------------------------------+
| **Tier III** <small>Lvl        | **Tier IV** <small>Lvl          |
| 60</small>                     | 75</small>                      |
|                                |                                 |
| Requires                       | Requires                        |
|                                |                                 |
| -   Tier II                    | -   Tier III                    |
| -   25 Essence                 | -   125 Essence                 |
| -   2 Meteoric Iron            | -   2 Ruby Heart                |
| -   2 Runestone                | -   2 Transport Stone           |
+--------------------------------+---------------------------------+
| **Tier V** <small>Lvl          | **Tier VI** <small>Lvl          |
| 90</small>                     | 105</small>                     |
|                                |                                 |
| Requires                       | Requires                        |
|                                |                                 |
| -   Tier IV                    | -   Tier V                      |
| -   375 Essence                | -   750 Essence                 |
| -   2 Blood Ruby               | -   2 Lump of Pure Adamantium   |
|                                | -   2 Sea Essence               |
+--------------------------------+---------------------------------+
| **Tier VII** <small>Lvl        | **Tier VIII** <small>Lvl        |
| 120</small>                    | 135</small>                     |
|                                |                                 |
| Requires                       | Requires                        |
|                                |                                 |
| -   Tier VI                    | -   Tier VII                    |
| -   1250 Essence               | -   2500 Essence                |
| -   2 Heart of Frost           | -   2 Stone of Heaven           |
| -   2 Lump of Pure Adamantium  |                                 |
+--------------------------------+---------------------------------+
| **Tier IX** <small>Lvl         | **Tier X** <small>Lvl           |
| 150</small>                    | 165</small>                     |
|                                |                                 |
| Requires                       | Requires                        |
|                                |                                 |
| -   Tier VIII                  | -   Tier IX                     |
| -   5000 Essence               | -   7500 Essence                |
| -   2 Blood Ruby               | -   2 Blood Ruby                |
| -   2 Stone of Heaven          | -   3 Stone of Heaven           |
+--------------------------------+---------------------------------+
| **Tier XI** <small>Lvl         |                                 |
| 180</small>                    |                                 |
|                                |                                 |
| Requires                       |                                 |
|                                |                                 |
| -   Tier X                     |                                 |
| -   10000 Essence              |                                 |
| -   Gemstone of the Olympians  |                                 |
| -   Gem of the North           |                                 |
| -   Gem of the East            |                                 |
| -   Gem of the South           |                                 |
| -   Gem of the West            |                                 |
+--------------------------------+---------------------------------+

For brevity, the changelog only presents the first and final tier stat
blocks.

+-----------------------------+-----------------------------+
| **Battleforge Regalia**     | **Divine Regalia**          |
|                             |                             |
| -   Strength: 25 → 75       | -   Strength: 20 → 70       |
| -   Agility: 10 → 60        | -   Intelligence: 15 → 65   |
| -   Attack Damage: 15 → 115 | -   Mana: 75 → 825          |
| -   Armor: 10 → 80          | -   Spell Power: 75 → 825   |
| -   Evasion I → Evasion V   | -   Armor: 5 → 35           |
|                             | -   Resist: 5 → 35          |
+-----------------------------+-----------------------------+
| **Wild Regalia**            | **Ironwood Regalia**        |
|                             |                             |
| -   Agility: 5 → 55         | -   Agility: 25 → 75        |
| -   Intelligence: 30 → 80   | -   Intelligence: 10 → 60   |
| -   Health: 100 → 1100      | -   Mana: 75 → 825          |
| -   Mana: 100 → 1100        | -   Spell Power: 75 → 825   |
| -   Spell Power: 100 → 1100 | -   Attack Damage: 25 → 175 |
+-----------------------------+-----------------------------+
| **Khaos Regalia**           | **Night Regalia**           |
|                             |                             |
| -   Strength: 25 → 75       | -   Strength: 5 → 55        |
| -   Agility: 10 → 60        | -   Agility: 30 → 80        |
| -   Health: 150 → 3000      | -   Flat Mana Regen: 1 \>   |
| -   Mana: 15 → 165          |     3.5                     |
| -   Armor: 10 → 60          | -   Attack Damage: 30 → 300 |
| -   Resist: 15 → 75         | -   Bloodthirsty            |
|                             | -   Night Set---Lethal      |
|                             |     Poison's AGI Ratio set  |
|                             |     to 4.0 → Lethal         |
|                             |     Poison's AGI Ratio set  |
|                             |     to 8.0                  |
+-----------------------------+-----------------------------+
| **Shadows Regalia**         | **Light Regalia**           |
|                             |                             |
| -   Intelligence: 35 → 135  | -   Strength: 5 → 55        |
| -   Flat Health Regen: 1 →  | -   Intelligence: 30 → 80   |
|     17.5                    | -   Spell Damage: 50 → 750  |
| -   Spell Damage: 125 →     | -   Spell Healing: 150 →    |
|     1375                    |     2250                    |
|                             | -   Mana Regeneration I →   |
|                             |     Mana Regeneration XI    |
+-----------------------------+-----------------------------+
| **Power Regalia**           | **Stone Regalia**           |
|                             |                             |
| -   Intelligence: 35 → 135  | -   Strength: 15 → 65       |
| -   Health: 50 → 1000       | -   Intelligence: 5 → 55    |
| -   Mana: 100 → 1500        | -   Health: 150 → 1500      |
| -   Spell Damage: 125 →     | -   Mana: 150 → 1500        |
|     1375                    | -   Spell Damage: 50 → 550  |
| -   Mana Regeneration I →   | -   Armor: 5 → 35           |
|     Mana Regeneration XI    | -   Resist: 25 → 125        |
+-----------------------------+-----------------------------+
| **Veteran's Regalia**       | **Deathbringer Regalia**    |
|                             |                             |
| -   Strength: 15 → 65       | -   Strength: 5 → 55        |
| -   Intelligence: 5 → 55    | -   Agility: 30 → 80        |
| -   Health: 150 → 1500      | -   Health: 150 → 1500      |
| -   Mana: 150 → 1500        | -   Attack Damage: 30 → 300 |
| -   Spell Power: 50 → 400   | -   Bloodthirsty            |
| -   Armor: 10 → 60          | -   Critical Strike 2.5     |
|                             | -   Deathbringer Set---Base |
|                             |     attack speed set to 1.6 |
|                             |     seconds → Base attack   |
|                             |     speed set to 1.5        |
|                             |     seconds                 |
+-----------------------------+-----------------------------+

## Attack Damage Aura Related Changes

*Bow of Artemis* <small>(Weaponsmith)</small>

-   No longer a Ranger only item
-   The damage bonus granted to ranged attacks was nerfed to 15% (from
    20%)
-   The AoE of the damage bonus granted to ranged attacks was nerfed to
    450 units (from 900 units)

> Increases Strength, Agility and Intelligence by 25 and Attack Damage
> by 50. Grants Trueshot Aura I.
>
> Trueshot Aura I---Gives allies within 450 units 15% bonus damage to
> their ranged attacks.
>
> Requires Level 85\
> Cannot be used by Warrior classes.

*Hunting Spear of Atalanta* <small>(Makarios)</small>

-   Previously known as *Hunting Spear of Artemis*
-   Increased attack damage was nerfed to 25 (from 45)
-   Updated its icon

> Increases Strength, Agility and Intelligence by 15, Attack Damage by
> 25 and Attack Speed by 25%.
>
> Requires Level 50\
> Cannot be used by Warrior classes.

*Boots of Marathon* <small>(Armorsmith)</small>

-   **Familiars**' can no longer use its active effect, Swift Return.

> Increases Strength by 50 and Movement Speed by 100. Grants 25% Evasion
> and Swift Return.
>
> Swift Return---Teleports you to Athens.\
> Cooldown: 3 minutes.
>
> Requires Level 85

*Hunting Garb of Atalanta* <small>(Metalsmith Arcadios)</small>

-   A new item crafted by **Metalsmith Arcadios** <small>(New
    Issus)</small> and requires:
    -   Boots of Marathon; Bow of Artemis; Hunting Spear of Atalanta;
        Gem of the South; Gem of the East; 3 Stone of Heaven; 2
        Transport Stone

> Increases Strength by 80, Agility and Intelligence by 40, Attack
> Damage by 75, Attack Speed by 25% and Movement Speed by 100. Grants
> 25% Evasion, Trueshot Aura II, and Swift Return.
>
> Trueshot Aura II---Gives allies within 450 units 25% bonus damage to
> their ranged attacks.
>
> Swift Return---Teleports you to Athens.\
> Cooldown: 3 minutes.
>
> Requires Level 150\
> Cannot be used by Warrior classes.

*Blade of Ares* <small>(Serpent of Hades)</small>

-   Level requirement increased to 75 (previously 55)
-   Attack damage bonus buffed to 75 (from 40)
-   Now grants Bloody Fervor I instead of regenerating 35 health per
    auto-attack

> Increases Attack Damage by 75 and Attack Speed by 30%. Grants Bloody
> Fervor.
>
> Bloody Fervor---Auto-attacks regenerate health equal to 1.5% of the
> damage dealt.
>
> Requires Level 75

*Sword of Might* <small>(Oceanus, Gaea)</small>

-   Previously known as *Sword of Command*
-   Level requirement increased to 75 (previously 40)
-   Srength and agility bonus buffed to 40 (from 10)
-   Attack damage bonus buffed to 45 (from 40)
-   The damage bonus is now only granted to melee attacks (previously
    all attacks)
-   The damage bonus granted to melee attacks was buffed to 15% (from
    10%)
-   The AoE of the damage bonus granted to melee attacks was nerfed to
    450 units (from 900 units)

> Increases Strength and Agility by 30, and Attack Damage by 45. Grants
> Might Aura I.
>
> Might Aura I---Gives allies within 450 units 15% bonus damage to their
> melee attacks.
>
> Requires Level 40

*Burning Hand of the War God* <small>(Goldsmith)</small>

-   Now grants Bloody Fervor I instead of "Auto-attacks regenerating
    health equal to 5% of the damage dealt"
-   No longer grants "Auto-attacks dealing 100 splash damage in an AoE:
-   Burning Hand of the War God <small>(Goldsmith)</small> crafting
    components changed to:
    -   2 Stone of Heaven; 2 Blood Ruby; 2 Ruby Heart.
        <small>(Previously 2 Stone of Heaven; 1 Blood Ruby; 1 Gemstone
        of Apollo; 2 Ruby Heart)</small>

> Increases Strength and Agility by 35, and Attack Speed by 30%. Grants
> Bloody Fervor I.
>
> Bloody Fervor I---Auto-attacks regenerate health equal to 1.5% of the
> damage dealt.
>
> Requires Level 85

*Ares' Blade of Might* <small>(Metalsmith Arcadios)</small>

-   Previously known as *Ares' Blade of Command*
-   Level requirement increased to 150 (previously 125)
-   Grants a strength and agility bonus of 65
-   Attack damage bonus buffed to 120 (from 90)
-   Grants Bloody Fervor II instead of regenerating 35 health per
    auto-attack
-   The damage bonus is now only granted to melee attacks (previously
    all attacks)
-   The damage bonus granted to melee attacks was buffed to 25% (from
    15%)
-   The AoE of the damage bonus granted to melee attacks was nerfed to
    450 units (from 900 units)
-   Crafting components changed to:
    -   Blade of Ares; Sword of Might; Burning Hand of the War God; Gem
        of the North; Gem of the West; 3 Stone of Heaven; 2 Ruby Heart.
        <small>(Previously Blade of Ares; Sword of Might; 2 Stone of
        Heaven; Gemstone of Apollo; 3 Heart of Frost)</small>

> Increases Strength and Agility by 65, Attack Damage by 120, and Attack
> Speed by 60%. Grants Bloody Fervor II and Might Aura II
>
> Bloody Fervor II---Auto-attacks regenerate health equal to 3% of the
> damage dealt.
>
> Might Aura II---Gives allies within 450 units 25% bonus damage to
> their melee attacks.
>
> Requires Level 150

*Sword of the High Commander* <small>(Champion's Armory)</small>

-   Updated the aura FX
-   No longer increases armor by 30
-   The AoE of the damage bonus granted to attacks was nerfed to 450
    units (from 900 units)

> Increases Strength and Agility by 50, and Attack Damage by 100. Grants
> Command Aura I.
>
> Command Aura I---Gives allies within 450 units 20% bonus damage to
> their attacks.
>
> Relic\
> Requires Level 180

*Thundering Hammer of Zeus* <small>(Master Metalsmith Heletes)</small>

-   Updated the aura FX
-   The damage bonus granted to attacks was nerfed to 30% (from 33%)
-   The AoE of the damage bonus granted to attacks was nerfed to 450
    units (from 900 units)

> Increases Strength and Agility by 150 and Intelligence by 5. Grants
> auto-attacks have a 6.5% chance to Break III the target for 3.25
> seconds reducing its Armor by 25, Command Aura II, and Chain
> Lightning.
>
> Command Aura II---Gives allies within 450 units 30% bonus damage to
> their attacks.
>
> Chain Lightning---Auto-attacks have a 15% chance to deal 4000 bonus
> magical damage, which then bounces to three other targets.
>
> Olympian Relic\
> Requires Level 200

# Forces of Hell

-   Adds in various boss fights no longer grant XP and Gold
-   *Lich* and *Cursed Weapon* <small>(The Fools' Mausoleum)</small> now
    play their decay animation after being slain
-   Whenever *Hallowed Offspring* <small>(Minotaur Burrows)</small>
    charges into a wall, they now are applied a debuff that causes it to
    take 35% more damage for the next 4 seconds
-   Adjusted the arena for *Goretusk*'s <small>(Tribal Village)</small>
    boss fight
-   *Pelias'* <small>(Southern Highlands)</small> drops changed to the
    following now that set items for each class have been removed:
    -   *High Oracle's Staff*; *High Oracle's Robes*; *Ring of Power*;
        and *Talisman of Wisdom*
-   *Neleus'* <small>(Southern Highlands)</small> drops changed to the
    following now that set items for each class have been removed:
    -   *Spartan Long Sword*; *Spartan Plate Mail*; *Ring of Might*;and
        *Amulet of Protection*
-   Updated the code that runs when you engage *Hallowed One*
    <small>(Minotaur Burrows)</small>, *Midas* <small>(The Fools'
    Mausoleum)</small>, *Manslayer* <small>(Minotaur Burrows)</small>
    and *Lightbane* <small>(Minotaur Burrows)</small>. This changes the
    acquisition range to 1500 units <small>(from 1000 units)</small> and
    now issues an attack-move order to the source of the damage *if*
    engagement occurs because of player characters
-   Updated the levels of the following bosses:
    -   Ladon <small>(Savage Jungle)</small>: 85 → 125
    -   Hydra <small>(Eretria)</small>: 75 → 100
    -   Serpent of Hades <small>(Isle of Issus)</small>: 60 → 75

## Titans

*Atlas*

> -   Lvl: 10 → 15
> -   Now becomes an interactive corpse upon death
> -   Once you're Level 30, you can interact with *Atlas*' corpse to
>     obtain *Titan Ore*

*Thea*

> -   Lvl: 15 → 30
> -   Updated model
> -   Now becomes an interactive corpse upon death
> -   Once you're Level 30, you can interact with *Thea's* corpse to
>     obtain *Titan Fibre*
> -   Additional item drops changed to the following:
>     -   *Boots of Agility*; *Gauntlets of Might*; *Robes of
>         Enlightenment*; *Orb of Mana Regeneration*; *Orb of Life
>         Regeneration*; *Medallion of Stamina*; *Pendant of Mana*; and
>         *Ring of Evasion\
>         *<small>(Previously: *Boots of Lesser Agility*; *Gauntlets of
>         Lesser Might*; *Robes of Lesser Enlightenment*; *Orb of Lesser
>         Mana Regeneration*; *Orb of Lesser Life Regeneration*;
>         *Medallion of Lesser Stamina*; *Pendant of Lesser Mana*; and
>         *Ring of Lesser Evasion*)</small>

*Themis*

> -   Lvl: 30 → 45
> -   Additional item drops changed to the following:
>     -   *Blade of the Chosen; Rod of the Chosen; Full Plate; Medallion
>         of Greater Stamina; Pendant of Greater Mana;* and *Robes of
>         the Chosen\
>         *<small>(Previously: *Boots of Agility; Gauntlets of Might;
>         Robes of Enlightenment; Ring of Evasion; Medallion of
>         Stamina;* and *Pendant of Mana*)</small>

*Cronus*

> -   Lvl: 40 → 60
> -   Additional item drops changed to the following:
>     -   *Medallion of Superior Stamina; Pendant of Superior Mana;
>         Surprisingly Good War Pick; Mage's War Staff; Voodoo Suit;*
>         and *Towering Shield\
>         *<small>(Previously: *Boots of Agility; Robes of
>         Enlightenment; Staff of Spell Power; Gauntlets of Might;
>         Champion's Blade;* and *Champion's Plate*)</small>

*Uranus*

> -   Lvl: 45 → 75
> -   Additional item drops changed to the following:
>     -   *Ripping Claws; Jeweled Ring; Adamantium Shield; Chestguard of
>         Aphrodite's Champion;* and *Talisman of the Winged God\
>         *<small>(Previously: *Champion's Blade; Boots of Agility;
>         Robes of Enlightenment; Champion's Plate;* and *Gauntlets of
>         Might*)</small>

*Rhea*

> -   Lvl: 55 → 90
> -   Item drops changed to the following:
>     -   *Ripping Claws; Jeweled Ring; Iron Will of Hephaestus;* and
>         *Shield of Warding\
>         *<small>(Previously Class set items)</small>

*Oceanus*

> -   Lvl: 70 → 105
> -   Additional item drops changed to the following:
>     -   *Shield of Warding; Aphrodite's Blessed Orb; Eris' Golden
>         Apple of Discord; Shield of Zeus;* and *Sword of Might\
>         *<small>(Previously: *Bone Wreath; Heart Blade; Eris' Golden
>         Apple of Discord; Myrmidon Scale;* and *Sword of
>         Might*)</small>

*Gaea*

> -   Lvl: 85 → 210
> -   Additional item drops changed to the following:
>     -   *Warrior's Talisman of Addiction; Talisman of Addiction; Eris'
>         Golden Apple of Discord; Iron Will of Hephaestus;* and *Sword
>         of Might.\
>         *<small>(Previously: *Bone Wreath; Heart Blade; Eris' Golden
>         Apple of Discord; Myrmidon Scale;* and *Sword of
>         Might*)</small>

## Sphinx

*Sphinx* now has contribution checkpoints. If the fight finishes and you
meet two of these checkpoints, you'll receive the crafting materials and
*Book of Skill Increase, Level 7* rewards even if you're not in
proximity of *Sphinx*.

-   When *Sphinx* reaches 50% of its Maximum HP
-   When *Sphinx* enters the *Vengeful Gaze* phase
-   When *Sphinx* enters the *Meteor* phase

## Resist Related Changes

<!--# Goretusk Furious Charge nerfed to 1400 magical damage (from 1875) Spike Barrage nerfed to 1125 magical damage (from 1500) Minotaur Warlock (Hallowed One add) now has an acquisition range of 1500 (from 1000) Helios' (Hyperion) Fire Blast mechanic now deals 2000 magical damage per tick (from 2500) Selene's (Hyperion) Meteor Shower mechanic now deals 24375 magical damage (from 30000) Theia's (Hyperion) Frost Nova mechanic now deals 8125 magical damage (from 10000) Eos' (Hyperion) Chain Lightning mechanic now deeals 6000 initial magical damage (from 7500) Hyperion The Nova mechanic now deals 20000 × (550 - d) / 450 magical damage, where d is the distance from the centre of the nova to the enumerated unit. (Previously the constant was 25000) The Thunder Bolt mechanic now deals 9750 magical damage (from 12000) Shadowslayer's Poison Sting mechanic now deals 300 magical damage per tick (from 500) Gaea's (Base Form) Thunder Bolt mechanic now deals 1625 magical damage (from 2000) and 812.5 AoE magical damage to all targets (from 1000)  -->

<!--# Note: These are all magical damage nerfs due to the new Resist stat introduced in the 20221217 build Gethos' Storm Bolt damage nerfed to 375.5 (from 500) Ice Giants' Ice Ring damage nerfed to 3250 (from 4000) Ladon's auto-attack damage nerfed to 4510–5500 (from 6518–7508) Hydra Breath of Fire initial damage nerfed to 1625 (from 2000) and Drunken Haze bonus DoT damage nerfed to 243.75 per tick (from 300) Shadow Strike initial damage nerfed to 812.5 (from 1000) and DoT damage nerfed to 406.25 per tick (from 500) Thea's mechanic where she casts Entangling Roots in retaliation has its DoT nerf to 150 per tick (from 220) Forest Terror's Shadow Strike damage nerfed to 130 (from 175) and DoT nerfed to 100 per tick (from 175) Rokthul's Chain Lightning initial damage nerfed to 375 (from 500) Nukacha's Chain Lightning initial damage nerfed to 93.75 (from 125) Minotaur Warlocks' Fireball damage nerfed to 1000 (from 1333) Soulesses' Frost Bolt damage nerfed to 300 (from 400) Tormenters' Chain Lightning damage nerfed to 262.5 (from 350) Goretusk Furious Charge damage nerfed to 1875 (from 2500) Spike Barrage damage nerfed to 1500 (from 2000) Cronus' Death Coil damage nerfed to 1500 (from 2000) Gethos' Geyser initial damage nerfed to 187.5 (from 250) and follow-up damage nerfed to 450 (from 600) Lucas Farblaze's Firebolt damage nerfed to 1500 (from 2000) Cyclops' Hurl Boulder damage nerfed to 1500 (from 2000) Hallowed One's and Hallowed Offsprings' Charge damage reduced to 1875 (from 2500) Manslayer's Deafening Bellow damage reduced to 1875 (from 2500) -->

## Stat Block Changes

A lot changes were made to the stat blocks of non-playerable characters
throughout the development of [1.39b7]{.underline}. The following
interactive table summarises all of them.

```{r}
#| include: false
library(googlesheets4); library(DT); library(dplyr)
bosses <- read_sheet("https://docs.google.com/spreadsheets/d/1IUeKLgC0J1M1xEdMZHyGvNMOoTf0CsICPGNkUDTAgpg/edit?usp=sharing", sheet = "Bosses / Minibosses") |> as.data.frame()
row.names(bosses) <- bosses[, 1]
bosses <- bosses[, -c(1, ncol(bosses))]

mobs <- read_sheet("https://docs.google.com/spreadsheets/d/1IUeKLgC0J1M1xEdMZHyGvNMOoTf0CsICPGNkUDTAgpg/edit?usp=sharing", sheet = "Mobs / Supermobs") |> as.data.frame()
row.names(mobs) <- mobs[, 1]
mobs <- mobs[, -c(1, ncol(mobs))]

wave <- read_sheet("https://docs.google.com/spreadsheets/d/1IUeKLgC0J1M1xEdMZHyGvNMOoTf0CsICPGNkUDTAgpg/edit?usp=sharing", sheet = "Wave") |> as.data.frame()
row.names(wave) <- wave[, 1]
wave <- wave[, -c(1, ncol(wave))]
```

::: panel-tabset
## Bosses / Minibosses

```{r}
#| echo: false
datatable(bosses, class = 'compact hover stripe')
```

## Mobs / Supermobs

```{r}
#| echo: false
datatable(mobs, class = 'compact hover stripe')
```

## Wave

```{r}
#| echo: false
datatable(wave, class = 'compact hover stripe')
```
:::
